The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2018-12-05 Ben_Manuscripts/transport/Outline.tex
Justifying CTRW
Updates

\title{The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts}

\begin{document}
%  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}
  \maketitle
  \section{Introduction}

@@

  A continuous time random walk (CTRW) is a stochastic process characterized by a 
  distribution of hop lengths and dwell times.
  \begin{itemize}
	\item We use the \texttt{ruptures} python package in order to identify
	breakpoints in solute trajectories. (See Supporting Information for more
	details on chosen parameters. i.e. type of cost function, cost function penalty
	tolerance, number of dimensions used)
	\item We have limited data, so we attempted to approximate these distributions
	with known continuous probability densities.
	\item For solutes in our system the distribution of hop lengths is
	well-represented by a Gaussian distribution while the distribution of dwell
	times fits relatively well to an exponential distribution characteristic of a
	Poisson process. (See supporting information)
  \end{itemize}

@@

>>>>

\title{The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia \and Michael R. Shirts}

\begin{document}

  \graphicspath{{./figures/}}
  \maketitle

  \section{Introduction}

@@

  A continuous time random walk (CTRW) is a stochastic process characterized by a 
  distribution of hop lengths and dwell times.
  \begin{itemize}
	\item We use the \texttt{ruptures} python package in order to identify
	breakpoints in solute trajectories. (See Supporting Information for more
	details on chosen parameters. i.e. type of cost function, cost function penalty
	tolerance, number of dimensions used)
	\item We have limited data, so we attempted to approximate these distributions
	with known continuous probability densities.
	\item Incorporates effects of `aging' since it samples long dwell times
	\item For solutes in our system the distribution of hop lengths is
	well-represented by a Gaussian distribution while the distribution of dwell
	times fits relatively well to an exponential distribution characteristic of a
	Poisson process. (See supporting information)
  \end{itemize}

@@

  Sodium ions also exhibit hop diffusion because polarized water and
  carboxylate head groups both work to neutralize its charge.
  \begin{itemize}
	\item Ions get trapped in oxygen 'cages' composed of combinations
	of water molecules, carboxylate head groups and ether oxygens connecting
	the head groups to their tails.
  	\item Interesting coordination number data
	\item Dwell time proportional to surrounding charge within coordination shell
  \end{itemize}

  \subsubsection*{Remarks}

  Overwhelming amount of water in 10 wt\% system makes hydrogen bonding
  competitive between head groups and water.

  \subsection{Design Suggestions}

  Water content affects pore size. Experiments to understand this could be useful.

  Separate polar molecules by creating monomers with more hydrophilic head group components.
  More incentive to dwell on walls.

  Make ions move faster by placing charges in sterically inaccessible places.
